Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-06-06 paper/paper.tex
clarify score averaging

Once both experts completed their annotation, we averaged their scores
we retained all IMTs whose \ml{relevance score averaged over experts} was judged equal to 3 or higher.
At the end of this stage of pre-screening, the list of IMT reduces from 235 to $N=78$.
Tables 1 and 2, in the Appendix section of this paper, give a full list of these 78 highly relevant IMTs.
It is worth noting that, according to both experts, the timbre of the accordion was judged too idiosyncratic, regardless of playing technique, to be relevant for this experiment.
Indeed, the accordion is the only instrument in the aforementioned list of
instrument to have free reeds, keyboard-based actuation, or handheld airflow.
Consequently, regardless of mute and technique, the set of instruments $\mathcal{I}$ in our study contains 15 elements.

>>>>

Once both experts completed their annotation, we ranked all 235 IMTs by decreasing average relevance score.
Then, we retained all IMTs whose average score was judged equal to 3 or higher, thus resulting in a shortlist of $N=78$ IMTs (see Tables 1 and 2 in the Appendix).
It is worth noting that, according to both experts, the timbre of the accordion was judged too idiosyncratic to be relevant for this experiment, regardless of playing technique.
Indeed, the accordion is the only instrument in the aforementioned list of
instrument to have free reeds, keyboard-based actuation, or handheld airflow.
Consequently, regardless of mute and technique, the set of instruments $\mathcal{I}$ in our study contains 15 elements.
